*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-03-20 inst/manuscript/manuscript.rmd
Switch from 'round' to 'signif';

```{r, echo = FALSE}
setwd(tmpDir)
max_PPR <- read.delim(
    "inputTable.txt",
    check.names = FALSE) %>%
  flippant:::calculatePpr() %>%
  max(
    na.rm = TRUE) %>%
  round(
    digits = 2
  )
```

@@

```{r, echo = FALSE}
setwd(tmpDir)
ppr_results <- scramblaseAssayStats("inputTable.txt", splitByExperiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  round(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblaseAssayStats`.")
```

@@

analysis_timing_median <- round(
  summary(
    analysis_timing)$median,
  2)

analysis_timing_iqr <- round(
  diff(
    unlist(
      summary(analysis_timing)[c("lq", "uq")],
      use.names = FALSE)),
  2)
```

>>>>

```{r, echo = FALSE}
setwd(tmpDir)
max_PPR <- read.delim(
    "inputTable.txt",
    check.names = FALSE) %>%
  flippant:::calculatePpr() %>%
  max(
    na.rm = TRUE) %>%
  signif(
    digits = 2
  )
```

@@

```{r, echo = FALSE}
setwd(tmpDir)
ppr_results <- scramblaseAssayStats("inputTable.txt", splitByExperiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  signif(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblaseAssayStats`.")
```

@@

analysis_timing_median <- signif(
  summary(
    analysis_timing)$median,
  2)

analysis_timing_iqr <- signif(
  diff(
    unlist(
      summary(analysis_timing)[c("lq", "uq")],
      use.names = FALSE)),
  2)
```
